---
title: "208275792_209014448"
author: "Jonathan Wiesenfeld & Rom Meltzer"
date: "`r Sys.Date()`"
output: html_document
---
## Prior Contents
Load Relevant libraries
```{r, warning=FALSE, message=FALSE} 
library(tidyverse) # This includes dplyr, stringr, ggplot2, .. 
library(data.table)
library(rworldmap) # world map
library(ggthemes)
library(reshape2) # melt: change data-frame format long/wide
library(e1071) # skewness and kurtosis
library(rvest)
library(dplyr)
library(corrplot) 
library(car) #From moodle forum
```

## Q1: Loading data and basic processing:
Loading the contents of "The Economist Democracy Index"; "List by Country", "List by Region", and "Components".
Use html_table to extract the individual tables from the all.tables object.
```{r}
url = 'https://en.wikipedia.org/wiki/The_Economist_Democracy_Index'
source = read_html(url)
all.tables = html_nodes(source, "table")  
list.by.region <- source %>%
  html_nodes(xpath = "/html/body/div[2]/div/div[3]/main/div[3]/div[3]/div[1]/table[3]") %>%
  html_table(fill =TRUE)
list.by.region <- as.data.frame(list.by.region[[1]])
list.by.country <- source %>%
  html_nodes(xpath = '//*[@id="mw-content-text"]/div[1]/table[5]') %>%
  html_table(fill = TRUE)
list.by.country <- as.data.frame(list.by.country[[1]])
components <- source %>%
  html_nodes(xpath = '//*[@id="mw-content-text"]/div[1]/table[6]') %>%
  html_table(fill=TRUE)
components <- as.data.frame(components[[1]])
components <- components[c(-1,-2,-27,-76,-113),-2]
head(list.by.region, 5)
head(list.by.country, 5)
head(components, 5)

``` 
## Q1b
Displaying the 5 top and bottom countries based on democracy index in 2022.

```{r}
bottom_five <- list.by.country %>% 
  arrange(desc(`2022 rank`)) %>% 
  select(`Country`, `2022 rank` ) %>% 
  head(5)

top_five <- list.by.country %>% 
  arrange(`2022 rank`) %>% 
  select(`Country`, `2022 rank`) %>% 
  head(5)
top_five
bottom_five

```
Repeat with average score between 2006 and 2022.
```{r}
avg.list<-rowMeans(list.by.country[5:length(list.by.country)])
avg.list.withcountry<-data.frame(Country=list.by.country$Country,avg.list)
sorted.alw <- avg.list.withcountry[order(avg.list.withcountry$avg.list, decreasing = TRUE), ]
avg_top_5 <- sorted.alw[1:5, ]
avg_bottom_5 <- sorted.alw[(nrow(sorted.alw)-4):nrow(sorted.alw), ]
avg_top_5
avg_bottom_5
```

## Q2: Plotting distributions of groups of countries:
We created boxplot for each region based on the distribution of _democracy index_. Calculated the outliers based on boxplot.stats; Israel and Turkey.
```{r}
boxplot(list.by.country$"2022" ~ list.by.country$Region,xlab="Regions",ylab="Index",main = "Democracy index Distribution")
regions<- list.by.country$Region %>% unique()

combined_list <- vector("list", length(regions))
for (i in 1:length(regions)) {
  region <- regions[i]
  data_vec <- list.by.country$"2022"[which(list.by.country$Region == region)]
  combined_list[[i]] <- data_vec
}
for(i in 1:length(regions)){
  if(boxplot.stats(combined_list[[i]])[4]!="numeric(0)"){
    for(j in boxplot.stats(combined_list[[i]])[4]){
      print(list.by.country$Country[which(list.by.country$"2022"==j)])
    }
  }
}

```
## Q2b
```{r}
ggplot(list.by.country, aes(x = `2022`, fill = Region)) +
  geom_density(alpha = 0.5) +
  labs(x = "Democracy Index (2022)", y = "Density") +
  ggtitle("Density Plots of Democracy Index by Region (2022)")
summary_stats <- list.by.country %>%
  group_by(Region) %>%
  summarise(
    Mean = mean(`2022`),
    Variance = var(`2022`),
    Skewness = skewness(`2022`),
    Kurtosis = kurtosis(`2022`)
  )

print(summary_stats)
```
Mean: The mean represents the average value of the democracy index for each region in 2022. It provides a measure of central tendency. For example, in the "North America" region, the mean democracy index is 8.36, indicating that, on average, countries in this region tend to have a higher democracy index compared to other regions.

Variance: The variance measures the spread or dispersion of the democracy index values within each region. A lower variance indicates that the values are clustered closer to the mean, while a higher variance suggests greater variability. For instance, the "North America" region has a variance of 0.530, indicating relatively low variability in the democracy index values compared to other regions.

Skewness: Skewness quantifies the asymmetry of the distribution. A skewness value close to 0 suggests a symmetric distribution, while positive or negative values indicate right-skewed or left-skewed distributions, respectively. For example, the "Middle East and North Africa" region has a positive skewness of 1.43, indicating that the democracy index values are skewed towards lower values.

Kurtosis: Kurtosis measures the shape of the distribution and describes the presence of heavy tails or outliers compared to a normal distribution. Positive kurtosis indicates a distribution with heavier tails and potentially more outliers, while negative kurtosis suggests a distribution with lighter tails. In the table, the "Western Europe" region has a high positive kurtosis of 3.93, indicating a distribution with heavy tails and potentially more extreme values (outliers).


## Q3: Comparing countries and showing trends in democracy index:
The code defines a function called plot_democracy_index_country that takes a data frame and a vector of country names as inputs. It subsets the data frame based on the provided country names and transforms the data into a long format. It then plots the democracy index values over time for the selected countries using different colors and line types. The function is used to plot the democracy index for five specific countries.
```{r}
#A function for listbycountry
plot_democracy_index_country <- function(data, names) {
  subset_data <- data[data$Country %in% names, ]
  grouping_column <- "Country"
  subset_data_long <- reshape2::melt(subset_data, id.vars = c("Country", "Region", "Regime type", "2022 rank"), variable.name = "Year", value.name = "DemocracyIndex")
  subset_data_long$Year <- as.integer(subset_data_long$Year)
  ggplot(subset_data_long, aes(x = Year, y = DemocracyIndex, color = get(grouping_column))) +
    geom_line() +
    labs(x = "Increase of Year from 2006", y = "Democracy Index", color = grouping_column, linetype = grouping_column) +
    ggtitle("Democracy Index Over Time") +
    theme(legend.title = element_blank())}

#A function for listbyregion

plot_democracy_index_region <- function(data, names) {
  subset_data <- data[data$Region %in% names, ]
  grouping_column <- "Region"
  subset_data <- subset_data[, c("Region", "2022", "2021", "2020", "2019", "2018", "2017", "2016", "2015", "2014", "2013", "2012", "2011", "2010", "2008", "2006")]
  subset_data_long <- reshape2::melt(subset_data, id.vars = "Region", variable.name = "Year", value.name = "DemocracyIndex")
  subset_data_long$Year <- as.numeric(subset_data_long$Year)
  ggplot(subset_data_long, aes(x = Year, y = DemocracyIndex, color = get(grouping_column), linetype = get(grouping_column))) +
    geom_line() +
    labs(x = "Increase of Year from 2006", y = "Democracy Index", color = grouping_column, linetype = grouping_column) +
    ggtitle("Democracy Index Over Time") +
    theme(legend.title = element_blank()) 
}
plot_democracy_index_region(list.by.region,c("North America","Western Europe","Latin America and the Caribbean","Asia and Australasia","Central and Eastern Europe","Sub-Saharan Africa","Middle East and North Africa" ))
plot_democracy_index_country(list.by.country,c("Canada","Israel","Iraq","Palestine","Norway"))
```
## Q3b
The code creates eight separate clusters of countries based on changes in the democracy index between 2006 and 2022. Each cluster is defined based on specific conditions such as the magnitude and direction of change. The resulting clusters are then used to create separate data frames for each cluster. The plot_democracy_index_country function is used to plot the democracy index over time for each cluster of countries.
```{r}
list.by.country$Change <- list.by.country$`2022` - list.by.country$`2006`
cluster1 <- list.by.country[list.by.country$Change >= 1.5, ]
cluster2 <- list.by.country[list.by.country$Change <= -1.5, ]
cluster3 <- list.by.country[list.by.country$Change >= 0.75 & list.by.country$Change <= 1.5, ]
cluster4 <- list.by.country[list.by.country$Change <= -0.75 & list.by.country$Change >= -1.5, ]
cluster5 <- filter(list.by.country,list.by.country$"2006" - apply(list.by.country[,5:19],1,min)>=0.75 & list.by.country$"2022"- apply(list.by.country[,5:19],1,min)>=0.75)
cluster6 <- filter(list.by.country,list.by.country$"2006" - apply(list.by.country[,5:19],1,max)<= -0.75 & list.by.country$"2022"- apply(list.by.country[,5:19],1,max)<= -0.75)
cluster7 <- filter(list.by.country, (apply(list.by.country[, 5:19],1,max) - apply(list.by.country[, 5:19], 1, min)) < 0.5)
lis<-c(cluster1$Country, cluster2$Country, cluster3$Country, cluster4$Country, cluster5$Country,cluster6$Country,cluster7$Country)
cluster8 <- list.by.country[!list.by.country$Country %in% lis,]
#clean the data and plot using the function
cluster1_data <- subset(cluster1, select = -c(Change))
cluster2_data <- subset(cluster2, select = -c(Change))
cluster3_data <- subset(cluster3, select = -c(Change))
cluster4_data <- subset(cluster4, select = -c(Change))
cluster5_data <- subset(cluster5, select = -c(Change))
cluster6_data <- subset(cluster6, select = -c(Change))
cluster7_data <- subset(cluster7, select = -c(Change))
cluster8_data <- subset(cluster8, select = -c(Change))

plot_democracy_index_country(cluster1_data, cluster1$Country)
plot_democracy_index_country(cluster2_data, cluster2$Country)
plot_democracy_index_country(cluster3_data, cluster3$Country)
plot_democracy_index_country(cluster4_data, cluster4$Country)
plot_democracy_index_country(cluster5_data, cluster5$Country)
plot_democracy_index_country(cluster6_data, cluster6$Country)
plot_democracy_index_country(cluster7_data, cluster7$Country)
plot_democracy_index_country(cluster8_data, cluster8$Country)
```

## Q4: Change in category
We created a helper function to determine type of demoocracy based on score, and then calculated the probability to move from one type of regime to another. The table is obviously not supposed to be symmetric.
See this table as move from row[j] to column[i]. e.g., move from Full Democracy to Flawed democracy is 0.0754.
```{r,warning=FALSE}
#helper function to determine type of regime for each country.
whichDemocracy<-function(num){
  ifelse(num>8 & num <=10,"Full democracy",
         ifelse(num>6 & num<=8, "Flawed democracy",
                ifelse(num>4 & num<=6,"Hybrid Regime","Authoritarian")))
  
}
data_2006 <- list.by.country$"2006"
data_2022 <- list.by.country$"2022"

empirical_changes<-function(old,new){
  regime.type<-c("Full democracy","Flawed democracy","Hybrid Regime","Authoritarian")
  result<-data.frame(matrix(0,nrow=4,ncol = 4,dimnames = c(regime.type %>% list(),regime.type %>% list())))
  for(i in 1:length(regime.type)){
    for(j in 1:length(regime.type)){
      to<-list.by.country$Country[which(whichDemocracy(data_2006)==regime.type[i])]
      from<-list.by.country$Country[which(whichDemocracy(data_2022)==regime.type[j])]
      val<-length(to[to%in%from])/length(to) 
      result[i,j]<-val
      
    }
  }
  return(result)
}

empirical_changes(data_2006,data_2022)

heatmap(empirical_changes(data_2006,data_2022)%>%as.matrix(),
        Rowv = NA,      # Disable row clustering
        Colv = NA,      # Disable column clustering
        scale = "none", # Do not scale the values
        main = "Empirical Changes",
        colnames = names,
        rownames = names)
```

## Q5: Joining data from additional tables
We added the new sources, and cleaned the data to match our specifications. For example, we change the column names for all tables that represent country names, to be only _"Country"_.
```{r,warning=FALSE}
url = "https://en.wikipedia.org/wiki/List_of_countries_by_GDP_(PPP)_per_capita"
source = read_html(url)
all.tables = html_nodes(source, "table")  
gdp.countries <- source %>%
  html_nodes(xpath = '//*[@id="mw-content-text"]/div[1]/table[1]') %>%
  html_table(fill =TRUE)
gdp.countries <- as.data.frame(gdp.countries[[1]])
colnames(gdp.countries)[1] <- "Country"
gdp.countries.clean<-gdp.countries[,c('Country',"CIA[8][9][10]")]
#INCARNATION
url = "https://en.wikipedia.org/wiki/List_of_countries_by_incarceration_rate"
source = read_html(url)
all.tables = html_nodes(source, "table")  
incarnation.rates <- source %>%
  html_nodes(xpath = '//*[@id="mw-content-text"]/div[1]/table[2]') %>%
  html_table(fill =TRUE)
incarnation.rates <- as.data.frame(incarnation.rates[[1]])
#AREA

url = "https://en.wikipedia.org/wiki/List_of_countries_and_dependencies_by_area"
source = read_html(url)
all.tables = html_nodes(source, "table")  
area <- source %>%
  html_nodes(xpath = '//*[@id="mw-content-text"]/div[1]/table[2]') %>%
  html_table(fill =TRUE)
area <- as.data.frame(area[[1]])

#POPULATION SIZE
url = "https://en.wikipedia.org/wiki/List_of_countries_and_dependencies_by_population"
source = read_html(url)
all.tables = html_nodes(source, "table")  
population <- source %>%
  html_nodes(xpath = '//*[@id="mw-content-text"]/div[1]/table[2]') %>%
  html_table(fill =TRUE)
population <- as.data.frame(population)
#Change the name of the column country
colnames(area)[2] = "Country"
colnames(population)[2] = "Country"
colnames(incarnation.rates)[1] = "Country"
colnames(gdp.countries)[1] = "Country"
#clean the names
incarnation.rates$Country= gsub("\\*", "", incarnation.rates$Country)
incarnation.rates$Country= gsub("\\ ","", incarnation.rates$Country)
incarnation.rates$Country= gsub("\\s", "", incarnation.rates$Country)
incarnation.rates$Country = gsub("\\[Note\\]", "", incarnation.rates$Country)
gdp.countries$Country= gsub("\\*", "", gdp.countries$Country)
gdp.countries$Country= gsub("\\ ","", gdp.countries$Country)
gdp.countries$Country= gsub("\\s","", gdp.countries$Country)
area$Country= gsub("\\ ", "", area$Country)
area$Country= gsub("\\(.*\\)", "", area$Country)
area$Country= gsub("\\s", "", area$Country)
population$Country= gsub("\\ ", "", population$Country)
population$Country= gsub("\\(.*\\)", "", population$Country)
population$Country= gsub("\\s", "", population$Country)
list.by.country$Country=gsub("\\ ", "", list.by.country$Country)
list.by.country$Country= gsub("\\(.*\\)", "", list.by.country$Country)


combined.table.GI=merge(gdp.countries,incarnation.rates)
combined.table.GIA=merge(combined.table.GI,area)
combined.table.GIAP=merge(combined.table.GIA,population,by="Country")
combined.table.GIAPL=merge(combined.table.GIAP,list.by.country,by="Country")

head(combined.table.GIAPL,5) 
```

## Q5b
Here we try to fit a regression line, firstly with "GDP per capita" (="CIA_reported") as the response, and lastly with "incarnation rates" as the response.
```{r,warning=FALSE}
CIA_reported <- as.numeric(gsub(",","",combined.table.GIAPL$`CIA[8][9][10]`))
incar_rate <- as.numeric(combined.table.GIAPL$`Rate per 100,000 [3]`)
data_2022 <- as.numeric(combined.table.GIAPL$`2022`)


gdp.by.rank<-lm(CIA_reported~data_2022) 
plot(data_2022,y = CIA_reported,xlab="2022 Rank",ylab = "GDP",main = "2022 Rank vs. CIA reported GDP")
abline(gdp.by.rank, col="Blue", lwd = 2)

gdp.by.incar<-lm(incar_rate~data_2022) 
plot(x=data_2022,incar_rate,xlab="2022 rank",ylab = "Incarnation rate",main = "Incarnation Rate vs. CIA reported GDP")
abline(gdp.by.incar, col="Blue", lwd = 2)
```

## Q6: Empirical Cumulative Distribution Function (CDF)
The code computes and plots the empirical cumulative distribution function (CDF) of the GDP (PPP) per capita for randomly selected countries. It first removes non-numeric characters from the CIA[8][9][10] column, converts it to numeric, and then uses the ecdf function to compute the empirical CDF. The resulting CDF is then plotted.
```{r}
# Compute the empirical CDF
combined.table.GIAPL$`CIA[8][9][10]`<-as.numeric(gsub("[^0-9.]","",combined.table.GIAPL$`CIA[8][9][10]`))
gdp=ecdf(combined.table.GIAPL$`CIA[8][9][10]`)
plot(gdp, main = "Empirical CDF of GDP (PPP) per capita", xlab = "GDP (PPP) per capita", ylab = "Empirical CDF")
```

## Q6b
The code computes and plots the empirical CDF of the GDP per capita for randomly selected individuals in the world. It calculates the GDP per capita by dividing the population size by the corresponding GDP values, sorts the values, and computes the empirical probabilities. The resulting CDF is plotted to show the cumulative probability distribution.
```{r}

combined.table.GIAPL$Population <- as.numeric(gsub("[^0-9.]","",combined.table.GIAPL$Population))
combined.table.GIAPL$`CIA[8][9][10]`<-as.numeric(gsub("[^0-9.]","",combined.table.GIAPL$`CIA[8][9][10]`))
gdp_per_capita <-combined.table.GIAPL$Population / combined.table.GIAPL$`CIA[8][9][10]`
gdp_per_capita.sort=sort(gdp_per_capita)
empirical_probs <- cumsum(combined.table.GIAPL$Population) / sum(combined.table.GIAPL$Population)
plot(gdp_per_capita.sort, empirical_probs, type = "s", main = "Empirical CDF of GDP per capita by population)",
     xlab = "GDP per capita", ylab = "Cumulative-Probability")
```

## Q6c
The code computes and plots the empirical CDF of the GDP per capita for randomly selected individuals based on their location within the land area on Earth. It removes non-numeric characters from the Landin km2 (mi2) column, converts it to numeric, and filters out the corresponding GDP per capita values based on valid indices. It then calculates the GDP per capita per unit of land area, computes the weighted empirical CDF using land area as weights, and plots the resulting CDF.

```{r}
#remove number in parentheses
converttochar<-as.character(combined.table.GIAPL$`Landin km2 (mi2)`)
cleaned_values <- gsub("\\s*\\([^)]+\\)|,", "", converttochar)
land_areakm2 <- as.numeric(cleaned_values)
#check for index that are not NA and match with the other vector
valid_indices <- !is.na(land_areakm2)
land_areakm2 <- land_areakm2[valid_indices]
# Filter the corresponding values from CIA[8][9][10] based on the same valid indices
gdp_per_capita <- as.numeric(gsub("[^0-9.]","",combined.table.GIAPL$`CIA[8][9][10]`))
gdp_per_capita <- gdp_per_capita[valid_indices]
# Calculate GDP per capita per unit of land area
gdp_per_capita_land <- gdp_per_capita / land_areakm2
# Compute weighted empirical CDF using land area as weights
empirical_probs_land <- cumsum(land_areakm2) / sum(land_areakm2)
# Plot the empirical CDF
plot(sort(gdp_per_capita_land), empirical_probs_land, type = "s", 
     main = "Empirical CDF of GDP per capita by land area",
     xlab = "GDP per capita per unit of land area", ylab = "Cumulative Probability")
```

## Q7: Displaying data on the world map

```{r, warning=FALSE, message=FALSE,echo=FALSE}
avg.list2<-rowMeans(list.by.country[5:length(list.by.country)])
map_list=bind_cols(list.by.country$Country,avg.list2)

colnames(map_list)[colnames(map_list) == "...1"] <- "Country"
colnames(map_list)[colnames(map_list) == "...2"] <- "average_democracy_index"

data("countryExData", package = "rworldmap")
merged_data <- joinCountryData2Map(map_list, joinCode = "NAME", nameJoinColumn = "Country")

world_map <- joinCountryData2Map(map_list, joinCode = 'NAME', nameJoinColumn = "Country", nameCountryColumn = "Country", suggestForFailedCodes = FALSE, mapResolution = "coarse", projection = NA, verbose = FALSE)

mapCountryData(world_map, nameColumnToPlot = "average_democracy_index", mapRegion = "world", colourPalette = "heat", addLegend = TRUE, borderCol = "black", mapTitle = "Average Democracy Index (2006-2022)", aspect = 1, missingCountryCol = NA, add = FALSE, nameColumnToHatch = "", lwd = 0.5)
```

Next, we plot the _changes_ in the democracy index between 2006 and 2022.

```{r}

#Changes in Index

change_in_years <- list.by.country$`2022` - list.by.country$`2006`
changes_map_list=bind_cols(list.by.country$Country,change_in_years)
colnames(changes_map_list)[colnames(changes_map_list) == "...1"] <- "Country"
colnames(changes_map_list)[colnames(changes_map_list) == "...2"] <- "Change_in_index"
world_map_changes <- joinCountryData2Map(changes_map_list, joinCode = 'NAME', nameJoinColumn = "Country",
                                 nameCountryColumn = "Country", suggestForFailedCodes = FALSE,
                                 mapResolution = "coarse", projection = NA, verbose = FALSE)

changes_map_list
mapCountryData(world_map_changes, nameColumnToPlot = "Change_in_index", mapRegion = "world", colourPalette = "heat",
               addLegend = TRUE, borderCol = "black", mapTitle = "Change of Democracy Index (2006-2022)",
               aspect = 1, missingCountryCol = NA, add = FALSE, nameColumnToHatch = "", lwd = 0.5)

```


# Q8a: Coponents of the Demography Index

```{r, warning=FALSE}
combined.table.GIAPLC <-merge(combined.table.GIAP,components,by="Country")
combined.table.GIAPLC %>% head(5)
ElectoralProccess <- as.numeric(combined.table.GIAPLC$`Elec­toral pro­cessand plura­lism`)
FunctioningOfGovernment <- as.numeric(combined.table.GIAPLC$`Func­tioningof govern­ment`)
PoliticalParticipation <- as.numeric(combined.table.GIAPLC$`Poli­ticalpartici­pation`)
PoliticalCulture <- as.numeric(combined.table.GIAPLC$`Poli­ticalcul­ture`)
CivilLiberties <- as.numeric(combined.table.GIAPLC$`Civilliber­ties`)

DemocracyComponents<-cbind(ElectoralProccess,FunctioningOfGovernment,PoliticalCulture,PoliticalParticipation,CivilLiberties)
DemocracyComponentsNames<-c("ElectoralProccess","FunctioningOfGovernment","PoliticalCulture","PoliticalParticipation","CivilLiberties")

CalcCor <- function(vec,titles){
  result<-data.frame(matrix(0,nrow=5,ncol = 5,dimnames = list(c(titles),c(titles))))
  for(i in 1:5){
    for(j in 1:5){
      result[i,j] <- cor(vec[,i],vec[,j])
    }
  } 
  return(result)
}

CalcCor(DemocracyComponents,DemocracyComponentsNames)

heatmap(CalcCor(DemocracyComponents,DemocracyComponentsNames)%>%as.matrix(),
        Rowv = NA,      # Disable row clustering
        Colv = NA,      # Disable column clustering
        scale = "none", # Do not scale the values
        main = "Democracy Components Corrolations",
        colnames = DemocracyComponentsNames,
        rownames = DemocracyComponentsNames)


```

## Q8b

```{r}

gdp.by.ElectoralProccess<-lm(CIA_reported~ ElectoralProccess+FunctioningOfGovernment+PoliticalCulture+PoliticalParticipation+CivilLiberties)
summary(gdp.by.ElectoralProccess)


coefficients <- coef(summary(gdp.by.ElectoralProccess))[, "Estimate"]
p_values <- coef(summary(gdp.by.ElectoralProccess))[, "Pr(>|t|)"]
significance_level <- 0.01

significant_coefficients <- coefficients[p_values < significance_level]
significant_coefficients


residuals <- rstudent(gdp.by.ElectoralProccess)
# Compute the 99th percentile of the residuals
percentile_99 <- quantile(residuals, 1-significance_level)
# Find the values in residuals that are bigger or smaller than the 99th percentile
outliers <- residuals[residuals > percentile_99 | residuals < -percentile_99]
outlier_countries <- combined.table.GIAPLC$Country[which(residuals>percentile_99 | residuals< -percentile_99)]
outlier_countries

residuals_table <- data.frame(Country = combined.table.GIAPLC$Country, Residuals = residuals)

top_outliers <- head(residuals_table[order(residuals_table$Residuals, decreasing = TRUE), ], 5)

bottom_outliers <- head(residuals_table[order(residuals_table$Residuals), ], 5)

outliers_table <- rbind(top_outliers, bottom_outliers)

#Other factors that may contribute to a country's GDP score is being part of an alliance,
# Such as NATO, or the UN. In addition, amount of natural resources the country have.



outliers_table
```